---
title: "Reproducible Quarto"
format: html
editor: visual
---
```{r}
#| message : false
library(tidyverse)
bond.data <- read_csv("data/jamesbond.csv")
bond.data
```

Which movie earned the most?
```{r}
##| cache : true
##| echo : false
##| output : false
profitable <- bond.data |>
    select(Year, Movie, US_Gross) |>
    arrange(desc(US_Gross))
profitable
```

The most profitable movie was `r profitable$Movie[1]`, made in `r profitable$Year[1]`. It made a profit of about `r (signif(profitable$US_Gross[1],1))/(10^6)` million.


`Is there a correlation between budget and earnings?`
```{r}
ggplot(bond.data, aes(x=Budget, y=US_Gross)) +
    geom_point()
# This doesn't account for inflation. Check: add colours for year?

ggplot(bond.data, aes(x=Budget, y=US_Gross, color=Year)) +
    geom_point() +
    scale_color_continuous()
```

`Definitely looks like year correlates with both earnings and budget.`
`The dataset contains inflation-adjusted numbers, let's use those instead.`

```{r}
ggplot(bond.data, aes(x=Budget_Adj, y=US_Adj, color=Year)) +
    geom_point() +
    scale_color_continuous()
```

`Still seems budget is increasing with year even after inflation adjustment, but the correlation with returns is now much less clear.`

`Just for fun: is there a correlation between the number of times` 
`Bond says "Bond, James Bond" and return??`

```{r}
ggplot(bond.data, aes(x=BJB, y=US_Adj)) +
    geom_point() +
    scale_color_continuous()
```

`It seems the movies earn more if he says it 0 or 2 times?`
`Probably a spurious correlation!`




